### 2022-11-01 CV2/general.tex
-

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
	&  Optimization\\
	& Federated and Distributed Learning\\
	&  Machine Learning
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, Jax, Pytorch\\
	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, HTML/CSS\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
\end{tabular}

>>>>

\section{Research Interests}
%Optimization Algorithms, Distributed Optimization, Machine Learning
\begin{tabular}{cl}
	&  Optimization, Federated and Distributed Learning\\
	&Machine Learning, Deep Learning
\end{tabular}

@@

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python, Algorithms and Data Structures, JAX, PyTorch\\
	& \textsc{Past experience:} Go, C\#, VB.NET, SQL, Julia, DirectX, Vulkan, HTML/CSS\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
	\textsc{Computer} & macOS, LaTeX, Git\\
%	\textsc{Languages} & English (Advanced), Russian (Native)
\end{tabular}
